%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Requires the Google Fonts "Source Sans Pro" and "Source Code Pro".
% You can install them on Linux using TypeCatcher.
% Must be compiled with XeLaTex to use the custom fonts (see the Makefile).
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Aakash}
\newcommand{\LastName}{Sharma}
\newcommand{\Initials}{A}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Me}{\textbf{\LastName, \Initials}}  % For citations
\newcommand{\Email}{aakash.sharma@uit.no}
\newcommand{\Website}{hysharma.com}
\newcommand{\ORCID}{0000-0003-3965-3271}
\newcommand{\Affiliation}{
    Department of Computer Science
    -- UiT - The Arctic University of Norway
}
\newcommand{\Address}{
    Hansine Hansens vei 54, Tromsø, 9019, Norway
}



% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Control the font size
\usepackage{anyfontsize}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}
\newcommand{\Invited}{[\textbf{Invited}] -- }

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
    \TablePad
    \begin{tabularx}{\textwidth}{@{}p{0.10\textwidth} p{0.9\textwidth}@{}}
        \BODY
    \end{tabularx}
}

% Macros to add links
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\Youtube}[1]{[recording: \href{https://youtu.be/#1}{youtu.be/#1}]}
% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont #1--#2}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
%\usepackage{fontspec}
%\setmainfont[BoldFont=SourceSansPro-Semibold]{SourceSansPro-Light}
%\setmonofont{Source Code Pro}

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.5cm}\bfseries\fontsize{12pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.2cm}\mdseries\fontsize{12pt}{0}\selectfont\uppercase}

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
    \itshape
    \fontsize{10pt}{12pt}\selectfont
    \MyName
    \hspace{0.2cm} -- \hspace{0.2cm}
    \Title
    \hspace{0.2cm} -- \hspace{0.2cm}
    \monthyear\today
}
\rhead{}
\cfoot{\fontsize{10pt}{0}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
    pdftitle={\MyName\ - \Title},
    pdfauthor={\MyName},
    linkcolor=blue,
    citecolor=blue,
    filecolor=black,
    urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
\begin{center}
    {\fontsize{24pt}{0}\selectfont \MyName}
    \\[0.5cm]
    {\fontsize{10pt}{0}\selectfont \Title \, | \, \monthyear\today}
    \\[0.5cm]
    {\fontsize{10pt}{0}\selectfont
        \Affiliation
        \\[0.2cm]
        \Address
        \\[0.08cm]
        ORCID: \href{http://orcid.org/\ORCID}{\ORCID}
        \, | \,
        \href{mailto:\Email}{\Email}
        \, | \,
        \href{http://\Website}{\Website}
    }
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}

\begin{EntriesTable}
    \Year{\textit{ongoing}}  &
    \textbf{Ph.D. in Computer Science}, UiT -- The Arctic University of Norway, Norway 
%    \newline
%    \newline
%    Thesis: \textit{Federated Privacy Policy Enforcement}
    \\
    \Year{2017}  &
    \textbf{M.Sc. in Distributed Software Systems}, Technische Universit{\"a}t Darmstadt, Germany
    \newline
    Thesis: \textit{Differential Map Updates for Highly Automated Driving and Enhanced Driver Assistance Services}
    \\
    \Year{2009}  &
    \textbf{B.Eng. in Information Technology}, Sant Gadge Baba Amravati University, India
    \\
    %\Year{2008}  &
    %\textbf{International Exchange}, York University, Canada
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional experience}

\begin{EntriesTable}
    \Duration{2017}{2021}  &
    \textbf{Ph.D. Candidate},
    UiT - The Arctic University of Norway, Norway
    \\
    \Duration{2016}{2017}  &
    \textbf{Student Employee},
    Polytech Domilens GmbH, Germany
    \\
    \Duration{2015}{2016}  &
    \textbf{Student Research Assistant},
    Ubiquitous Knowledge Processing (UKP) Lab, Technische Universit{\"a}t Darmstadt, Germany      
    \\
    \Duration{2013}{2014}  &
    \textbf{Web Developer},
    Digital India Corporation (\textit{formerly} Media Lab Asia), India
    \\
    \Duration{2010}{2013}  &
    \textbf{Systems Software Engineer},
    IBM India Software Labs, India
    \\
    \Duration{2009}{2010}  &
    \textbf{Software Engineer},
    Persistent Systems, India
    \\
    \Duration{2009}{2009}  &
    \textbf{Trainee},
    Persistent Systems, India
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\section*{Honors \& Awards}
%
%\begin{EntriesTable}
%    \Year{2018}  &
%    Reading Group Competition at ICVSS 2018
%\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Publications}
\iffalse

Source code, data, and PDFs for most articles are available
at \href{http://www.leoSharma.com/papers}{leoSharma.com/papers}
\fi
\iffalse

\subsection*{Peer-Reviewed}


\begin{EntriesTable}
\Year{In prep.}  &
    \Santiago, \Agustina, \Me, \Gimenez.
    Tesseroid gravity field calculations using variable densities in depth.
    \\
    ~ &
    Zhao, G, Liu, J, \Me, Chen, B, Guo, R, Chen, L.
    A fast algorithm for forward modeling of gravitational fields in
    spherical coordinates with 3D Gauss-Legendre Quadrature.
    \\
%\Year{Review}  &
    %\\
\Year{2017}  &
    \Me, \Val.
    Fast non-linear gravity inversion in spherical coordinates with application
    to the South American Moho,
    \emph{Geophysical Journal International},
    \DOI{10.1093/gji/ggw390}.
    \\
\Year{2016}  &
    \Me, \Val, \Carla.
    Tesseroids: forward modeling gravitational fields in spherical coordinates,
    \emph{Geophysics},
    \DOI{10.1190/geo2015-0204.1}.
    \\
    ~ &
    \Dio, \Me, \Val.
    How two gravity-gradient inversion methods can be used to reveal different
    geologic features of ore deposit - A case study from the Quadrilátero
    Ferrífero (Brazil),
    \emph{Journal of Applied Geophysics},
    \DOI{10.1016/j.jappgeo.2016.04.011}.
    \\
\Year{2015}  &
    \Bi, \Dai, \Val, \Me.
    Estimation of the total magnetization direction of approximately spherical
    bodies,
    \emph{Nonlinear Processes in Geophysics},
    \DOI{10.5194/npg-22-215-2015}.
    \\
\Year{2014}  &
    \Dio, \Me, \Val.
    Imaging iron ore from the Quadrilátero Ferrífero (Brazil) using geophysical
    inversion and drill hole data,
    \emph{Ore Geology Reviews},
    \DOI{10.1016/j.oregeorev.2014.02.011}.
    \\
\Year{2013}  &
    \Figura, \Val, \Me, \Bi, \JB.
    Estimating the nature and the horizontal and vertical positions of 3D
    magnetic sources using Euler deconvolution,
    \emph{Geophysics},
    \DOI{10.1190/geo2012-0515.1}.
    \\
    ~ &
    \Bi, \Val, \Me.
    Polynomial equivalent layer,
    \emph{Geophysics},
    \DOI{10.1190/geo2012-0196.1}.
    \\
\Year{2012}  &
    \Me, \Val.
    Robust 3D gravity gradient inversion by planting anomalous densities,
    \emph{Geophysics},
    \DOI{10.1190/geo2011-0388.1}.
\end{EntriesTable}
\fi

%\subsection*{Peer-Reviewed Conference proceedings}
\begin{EntriesTable}
	\Year{\textit{2021} \textit{-- Accepted}}  &
\textbf{Aakash Sharma}, Thomas Bye Nilsen, Lars Brenna, Dag Johansen and H{\aa}vard D. Johansen.
Accountable Human Subject Research Data Processing using Lohpi,
\emph{Proceedings of the International Conference on ICT enhanced Social Sciences and Humanities (ICTeSSH)}. 
%\DOI{10.2196/19085}

\\
	\Year{\textit{2020}}  &
	\textbf{Aakash Sharma}, Katja P. Czerwinska, Lars Brenna, Dag Johansen, H{\aa}vard D. Johansen.
Privacy Perceptions and Concerns in Image-Based Dietary Assessment Systems: Questionnaire-Based Study,
	\emph{JMIR Hum Factors}
	\DOI{10.2196/19085}.
	\\
	
\Year{\textit{2019}}  &
    Florian Jomrich, \textbf{Aakash Sharma}, Tobias R{\"u}ckelt, Doreen B{\"o}hnstedt, Ralf Steinmetz.
    Intelligent Offloading Distribution of High Definition Street Maps for Highly Automated Vehicles,
    \emph{Smart Cities, Green Technologies, and Intelligent Transport Systems, Springer, Cham}
   \DOI{10.1007/978-3-030-02907-4\_11}.
   \\
\Year{2017}  &
    Florian Jomrich, \textbf{Aakash Sharma}, Tobias R{\"u}ckelt, Daniel Burgstahler, Doreen B{\"o}hnstedt.
    Dynamic Map Update Protocol for Highly Automated Driving Vehicles,
    \emph{Proceedings of the International Conference on Vehicle Technology and Intelligent Transport Systems (VEHITS)},
    \DOI{10.5220/0006279800680078}.
    \\
\end{EntriesTable}




\iffalse

\subsection*{Open Datasets}

\begin{EntriesTable}
\Year{2017}  &
    \Me, \Val.
    A gravity-derived Moho model for South America: source code, data, and
    model results from ``Fast non-linear gravity inversion in spherical
    coordinates with application to the South American Moho''.
    \DOI{10.6084/m9.figshare.3987267}
\end{EntriesTable}
\fi

\subsection*{Open-source Software}
\textbf{WebAnno} 3.0 -- \href{https://webanno.github.io/webanno/}{https://webanno.github.io/webanno/}
\\
A Flexible, Web-based and Visually Supported System for Distributed Annotations
%\\[0.3cm]
\iffalse
\\
\textbf{osm2pgrouting} -- \href{https://github.com/aakashysharma/osm2pgrouting}{https://github.com/aakashysharma/osm2pgrouting}
\\
Import tool for OpenStreetMap data to pgRouting database including version and timestamp
\\[0.3cm]

\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection*{Teaching}

%All educational material developed for these courses is available at
%\href{http://www.leoSharma.com/teaching}{leoSharma.com/teaching}

%\subsection*{Undergraduate -- Universidade do Estado do Rio de Janeiro}

\begin{EntriesTable}
	\Year{Fall '20, '19} &
	INF-3200: Distributed Systems Fundamentals
	\\
	\Year{Spring '20} &
	INF--3203: Advanced Distributed Systems 
%	\\
%    \Year{Fall 2019}  &
%    INF--3200: Distributed Systems Fundamentals
%    \\
%    \Year{Spring 2020} &
%    INF--3203: Advanced Distributed Systems
%    \\
%    \Duration{2014}{2016}  &
%    Geophysics I: Gravity and magnetic methods
%    \\
%    \Duration{2014}{2016}  &
%    Geophysics II: Exploration Seismology
%    \\
%    \Year{2015}  &
%    Introduction to Geology
\end{EntriesTable}


\subsection*{Workshops and Schools} % and Short Courses}

\begin{EntriesTable}
	\Year{2020} &
	2$^{nd}$ Human Behavior and Machine Intelligence (HUMAINT) Winter School
	\\
\Year{2018}  &
	1$^{st}$ ACM SIGOPS Summer School on Advanced Topics in Systems (SATIS)
%	    \newline
%	Troms{\o}, Norway
\\
\Year{2018}  &
	12$^{th}$ International Computer Vision Summer School (ICVSS)
%	    \newline
%	Sicily, Italy
\\
\Year{2018}  &
	12$^{th}$ European Conference on Computer Systems (EuroSys) Doctoral Workshop
%	    \newline
%	Porto, Portugal
\\
\Year{2017}  &
    2$^{nd}$ International Workshop on Personal Data Systems (PDS)
%    \newline
%    Department of Computer Science, University of Troms{\o},
%    Sommar{\o}y, Norway
%    \\
\end{EntriesTable}

\iffalse

\begin{EntriesTable}
\Year{2017}  &
    Introduction to Python (6 hour workshop)
    \newline
    Department of Geology and Geophysics -- University of Hawaii at Manoa,
    USA
    \\
\Year{2016}  &
    Python for Geologists (6 hour workshop)
    \newline
    School of Geology -- Universidade do Estado do Rio de Janeiro, Brazil
    \\
    ~  &
    Python for Earth Scientists (30 hour short course)
    \newline
    Department of Geophysics -- Universidade de São Paulo, Brazil
    \\
\Year{2014}  &
    Introduction to Geophysical Inversion (16 hour short course)
    \newline
    Institute of Geosciences -- Universidade de Brasília, Brazil
    \\
\Year{2011}  &
    Introduction to Geophysical Inversion (30 hour short course)
    \newline
    Department of Geophysics -- Universidade de São Paulo, Brazil
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Presentations}

Slides, posters, and abstracts for all presentations are available at
\href{http://www.leoSharma.com/talks/}{leoSharma.com/talks}
and
\\
\href{http://www.leoSharma.com/posters/}{leoSharma.com/posters}
\\
\begin{EntriesTable}
%\Year{Future}  &
\Year{2017}  &
    \Invited{}
    \Me, et al.
    Nurturing reliable and robust open-source scientific software,
    \emph{AGU Fall Meeting 2017},
    New Orleans, USA.
    \\
    ~  &
    \Me, et al.
    A modern Python interface for the Generic Mapping Tools,
    \emph{AGU Fall Meeting 2017},
    New Orleans, USA.
    \\
    ~  &
    \Me, et al.
    Bringing the Generic Mapping Tools to Python,
    \emph{Scipy 2017},
    Austin, USA.
    \Youtube{93M4How7R24}
    \\
    ~ &
    \Me.
    Inverting gravity to map the Moho: A new method and the open source
    software that made it possible,
    \emph{University of Hawaii},
    Honolulu, USA.
    \\
\Year{2016}  &
    \Invited{}
    \Me.
    Fatiando a Terra: construindo uma base para ensino e pesquisa de geofísica,
    \emph{Observatório Nacional},
    Rio de Janeiro, Brazil.
    \\
\Year{2015}  &
    \Invited{}
    \Me.
    Fatiando a Terra: construindo uma base para ensino e pesquisa de geofísica,
    \emph{Universidade de São Paulo},
    São Paulo, Brazil.
    \\
\Year{2014}  &
    \Me, et al.
    Using Fatiando a Terra to solve inverse problems in geophysics,
    \emph{Scipy 2014},
    Austin, USA.
    \\
    ~ &
    \Me, et al.
    Gravity inversion in spherical coordinates using tesseroids,
    \emph{EGU General Assembly 2014},
    Vienna, Austria.
    \\
\Year{2013}  &
    \Me, et al.
    Modeling the Earth with Fatiando a Terra,
    \emph{Scipy 2013},
    Austin, USA.
    \Youtube{Ec38h1oB8cc}
    \\
    ~ &
    \Me, et al.
    3D magnetic inversion by planting anomalous densities,
    \emph{AGU Meeting of the Americas},
    Cancun, Mexico.
    \\
\Year{2012}  &
    \Dio, \Me, et al.
    Iron ore interpretation using gravity-gradient inversions in the Carajás,
    Brazil,
    \emph{SEG Annual Meeting 2012},
    Las Vegas, USA.
    \\
    ~ &
    \Me, et al.
    Use of the ``shape-of-anomaly'' data misfit in 3D inversion by planting
    anomalous densities,
    \emph{SEG Annual Meeting 2012},
    Las Vegas, USA.
    \\
    ~ &
    \Me, et al.
    Rapid 3D inversion of gravity and gravity gradient data to test geologic
    hypotheses,
    \emph{International Symposium on Gravity, Geoid and Height Systems},
    Venice, Italy.
    \\
\Year{2011}  &
    \Me, et al.
    Robust 3D gravity gradient inversion by planting anomalous densities,
    \emph{SEG Annual Meeting 2011},
    San Antonio, USA.
    \\
    ~ &
    \Me, et al.
    3D gravity inversion by planting anomalous densities,
    \emph{Internation Congress of the Brazilian Geophysical Society},
    Rio de Janeiro, Brazil.
    \\
    ~ &
    \Me, et al.
    Optimal forward calculation method of the Marussi tensor due to a geologic
    structure at GOCE height,
    \emph{4th International GOCE User Workshop},
    Munich, Germany.
    \\
    ~ &
    \Me, et al.
    3D gravity gradient inversion by planting density anomalies,
    \emph{73th EAGE Conference and Exhibition incorporating SPE EUROPEC},
    Vienna, Austria.
    \\
\Year{2010}  &
    \Me, et al.
    Computation of the gravity gradient tensor due to topographic masses using
    tesseroids,
    \emph{AGU Meeting of the Americas},
    Foz do Iguaçu, Brazil.
    \\
\Year{2008}  &
    \Me, et al.
    Utilização de tesseróides na modelagem de dados de gradiometria
    gravimétrica,
    \emph{XIII Simpósio de Iniciação Científica do IAG-USP},
    São Paulo, Brazil.
    \\
\Year{2006}  &
    \Me, et al.
    Paleomagnetismo e mineralogia magnética dos diques cambrianos de Maravilhas
    e Prata (PB),
    \emph{XI Simpósio de Iniciação Científica do IAG/USP},
    São Paulo, Brazil.
\end{EntriesTable}

\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Academic Service}

%\subsection*{Committees}

\begin{EntriesTable}
%	\Year{2020} & \textbf{Board Member} The Association of Doctoral Organisations in Norway
%	\\
	\Year{2018--2021} & \textbf{Member} ACM SIGOPS Social Media Team
    \\
    \Year{2020}& \textbf{Shadow PC} European Conference on Computer Systems (EuroSys) 2020 
    \\
    \Year{2019} & \textbf{Reviewer} \textit{Special Issue on Emerging Soft Computing Methodologies in Deep Learning and Applications}, Applied Soft Computing (Elsevier)
    \\
    \Year{2019} & \textbf{Artifact Evaluation Committee} ACM SOSP
    \\
    \Year{2018--2019} & \textbf{Vice Board-Chair} Doctoral Students at UiT -- The Arctic University of Norway% (TODOS)
    \\
    \Year{2018} & \textbf{Poster Chair} 1$^{st}$ ACM SIGOPS Summer School on Advanced Topics in Systems
    \\
    \Year{2016} & \textbf{Student Volunteer} ISC High Performance Conference%, Frankfurt, Germany 
\end{EntriesTable}


\iffalse

\subsection*{Reviewer}

Geophysical Journal International
--
Journal of Geodesy
--
Pure and Applied Geophysics
--
Journal of Applied Geophysics
--
Geophysical Prospecting
--
Geophysics
--
Central European Journal of Geosciences
--
Computers \& Geosciences

\fi
\iffalse

\subsection*{Affiliations}

American Geophysical Union
--
Society of Exploration Geophysicists
--
Geological Society of America

\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Languages}
English (\textit{Fluent}), Norwegian (\textit{Intermediate}), German (\textit{Basic}), Hindi (\textit{Native})
%\TablePad
%\begin{tabularx}{\textwidth}{@{}p{0.25\textwidth} p{0.75\textwidth}@{}}
% %   Hindi & Native
%  %  \\
%    English & Fluent %(IELTS 7.5/9.0)
%    \\
%    German & Basic %reading and listening
%    \\
%    Norwegian & Basic
%    %\\
%    %Hindi & Native
%    %Norwegian Bokmal & Basic
%\end{tabularx}

\end{document}
